Title Goes Here

### 2020-04-10 analysis/paper/paper.Rmd
editing PCA

#group them by three phase
library(ggfortify) 
ap <- 
autoplot(prcomp(DF, center = TRUE, scale = TRUE), 
         data = df_sitename, 
         colour = as.factor(df_sitename$SPstage.Stage))

pca_col <- data.frame(PCA$x, phase = as.factor(df_sitename$SPstage.Stage))

gg <- 
ggplot(pca_col ,
       aes(PC1,
           PC2,
       colour = phase)) +
  geom_point()

gg

@@

xx_pca1 <- data.frame(xx_pca$x,stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage !=1]))

@@

>>>>

#group them by three phase
library(ggfortify)

@@

xx_pca1 <- 
  data.frame(xx_pca$x,
             stage = as.factor( df_sitename$SPstage.Stage[df_sitename$SPstage.Stage !=1]))

@@

library(factoextra) #http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/112-pca-principal-component-analysis-essentials/

fviz_pca_var(xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))
